---
title: "p8105_hw1_LL3407"
output: github_document
date: "2022-09-18"
---
# Problem 1

```{r, echo=FALSE}
data("penguins",package="palmerpenguins")
library(tidyverse)
library(dplyr)
```
## Discription of _penguins_
* The dataset _penguins_ contains 8 variables, inlcuding species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year.  
* There are 344 observations in _penguins_.  
* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

## Scatterplot of flipper length vs bill length
```{r}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species))+geom_point()

ggsave("scplot_bill+flipper.pdf")
```

# Problem 2  
## Create a dataframe
```{r, echo=FALSE}
dataframe=tibble(
  var_norm=rnorm(n=10),
  var_lg=var_norm>0,
  var_char=c(length(10)),
  var_fc=factor(sample(c(1,2,3),10,replace=T),levels=c("1","2","3"))
  )

```

* The mean of random sample is `r mean(pull(dataframe, var_norm))`.  
* The mean of logic vector is `r mean(pull(dataframe, var_lg))`.
* The mean of character vector is `r mean(pull(dataframe, var_char))`.
* The mean of factor vector is `r mean(pull(dataframe, var_fc))`.

The code of mean works for random sample, logic vector, and character vector, but not for factor vector.


## Convert logic, character and factor variables to numeric varaibles.

```{r, eval=FALSE}
as.numeric(pull(dataframe,var_lg))
as.numeric(pull(dataframe,var_char))
as.numeric(pull(dataframe,var_fc))
```

* The logic variables are the number of "0" or "1", and the character variables are the number of "1" after converting to the numeric variables. The number "0" or "1" can be recognized by computer, so the mean code works for those two kinds of variable. However, the factor variables are from "1" to "3" after converting to numeric variables. Number "2" or "3" cannot be recognized by computer, so the mean code doesn't work for factor variables. 


