---
title: "p8105_hw1_LL3407"
output: github_document
date: "2022-09-18"
---
# Problem 1

```{r, echo=FALSE}
data("penguins",package="palmerpenguins")
library(tidyverse)
library(dplyr)
```
## Discription of _penguins_
* The dataset _penguins_ contains 8 variables, inlcuding species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year.  
* There are 344 observations in _penguins_.  
* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

## Scatterplot of flipper length vs bill length
```{r}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species))+geom_point()

ggsave("scplot_bill+flipper.pdf")
```

# Problem 2  
## Create a dataframe
```{r, echo=FALSE}
dataframe=tibble(
  var_norm=rnorm(n=10),
  var_lg=var_norm>0,
  var_char=c(length(10)),
  var_fc=factor(sample(c(1,2,3),10,replace=T),levels=c("1","2","3"))
  )

```

* The mean of random sample is `r mean(pull(dataframe, var_norm))`.  
* The mean of logic vector is `r mean(pull(dataframe, var_lg))`.
* The mean of character vector is `r mean(pull(dataframe, var_char))`.
* The mean of factor vector is `r mean(pull(dataframe, var_fc))`.

The code of mean works for random sample, but not for logic vector, character vector, or factor vector despite the mean values from logic vector and character vectors.


## Convert logic, character and factor variables to numeric varaibles.

```{r, eval=FALSE}
as.numeric(pull(dataframe,var_lg))
as.numeric(pull(dataframe,var_char))
as.numeric(pull(dataframe,var_fc))
```




